---
title: "Multiple Regression"
author: "Mohit Garg"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading data form the csv file

```{r}
data <- read.csv('/Users/mohit/Development/My Scripts/modelsEvaluation.csv',stringsAsFactors= T)
summary(data)
```

## Preprocessing the data
Replacing all the NaN with the mean value. 

```{r}
data$NT = ifelse(is.na(data$NT), ave(data$NT, FUN = function(x) mean(x, na.rm = TRUE)),data$NT)
data$INT_ALY = ifelse(is.na(data$INT_ALY), ave(data$INT_ALY, FUN = function(x) mean(x, na.rm = TRUE)),data$INT_ALY)
data$INT = ifelse(is.na(data$INT), ave(data$INT, FUN = function(x) mean(x, na.rm = TRUE)),data$INT)
data$DM = ifelse(is.na(data$DM), ave(data$DM, FUN = function(x) mean(x, na.rm = TRUE)),data$DM)
data$CTRL = ifelse(is.na(data$CTRL), ave(data$CTRL, FUN = function(x) mean(x, na.rm = TRUE)),data$CTRL)
data$EXTCLL = ifelse(is.na(data$EXTCLL), ave(data$EXTCLL, FUN = function(x) mean(x, na.rm = TRUE)),data$EXTCLL)
data$EXTIVK = ifelse(is.na(data$EXTIVK), ave(data$EXTIVK, FUN = function(x) mean(x, na.rm = TRUE)),data$EXTIVK)
```

## Preparing the independent variables
1. Removing all the variables with zero value for all the observations. 
2. Facorizing the type variable
3. Calculating the corelation between all the independent and dependent variables.
4. Choosing all the variables with highest corelation values. 

```{r}
x <-data[,7:45];
x$Type = factor(x$Type, levels = c('Web App', 'Mobile App', 'Mobile&Web App'),labels = c(1,2,3))
x$ILF<-NULL
x$EIF<-NULL
x$DET<-NULL
x$EF_ALY<-NULL
x$TCF_ALY<-NULL
x$Type[5] = 1
x$Type[7] = 1
x$Type[20] = 3
x$Type = as.numeric(x$Type)

y =data$Effort
summary(x)
```

## Correlation 
Calculating the correlation and choosing the independent variables with correlation higher than 0.6 with the dependent variable (Effort).

``` {r}
corr <- cor(x,y)
plot(corr,xlim=c(0, 36))
text(1:35,corr,row.names(corr),cex=0.4, pos=4, col="blue")
abline(h=0.6,col="red")
```

Looking at the graph, following are the most correlated independent variables:  
1. KSLOC  
2. UEUCW_ALY  
3. UEXUCW_ALY  
4. UDUCW_ALY  
5. Effort_Norm_UCP  
6. Path_Num  
7. DUCP_ALY  
8. EXUCP_ALY  
9. EUCP_ALY  
10. UseCase_Num  
11. Diagram_Num  
12. INT_ALY  
13. DM_ALY  
14. CTRL_ALY  
15. NT_ALY  
16. NWT_DE_ALY  
17. NWT_ALY  
  

## Model Fitting

Using all the above variables except UseCase_NUM and Diagram_Num for fitting the model.  

```{r}
independentVar <- data.frame(x$KSLOC,x$UEUCW_ALY,x$UEXUCW_ALY,x$UDUCW_ALY,x$Effort_Norm_UCP,x$Path_Num,x$DUCP_ALY,x$EXUCP_ALY,x$EUCP_ALY,x$INT_ALY,x$DM_ALY,x$CTRL_ALY,x$NWT_DE_ALY,x$NWT_ALY)

names(independentVar)<- c("KSLOC","UEUCW_ALY","UEXUCW_ALY","UDUCW_ALY","Effort_Norm_UCP","Path_Num","DUCP_ALY","EXUCP_ALY","EUCP_ALY","INT_ALY","DM_ALY","CTRL_ALY","NWT_DE_ALY","NWT_ALY")

#library(caret)
#set.seed(30)
#model <- train(y~.,data=independentVar,method="lm",trControl = trainControl(method = "cv", number=2,verboseIter = TRUE))

fit <- lm(y~.,data=independentVar)
summary(fit)
```


