---
title: "Transaction Weight Calibration Visualized"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("utils/feature_selection.R")
source("utils/data_selection.R")
source("utils/model_funcs.R")
source("accuracy_confidence_evaluation.R")
source("transaction_based_model.R")
source("size_metric_based_models.R")
source("neuralnet_model_2.R")
source("stepwise_linear_model.R")
source("lasso_regression_model3.R")
source("regression_tree_model_8_7.R")
source('familywiseHypoTest2.R')
library(jsonlite)
library(reshape)
library(tidyverse)
library(fitdistrplus)
library(egg)
library(gridExtra)
library(plyr)
library(lsr)
require(MASS)

```
Combined Data Effort Values
```{r descriptive statistics, fig.width=5,fig.height=2.5}
#The previous dataset
#modelData <- selectData("dsets/modelEvaluations-1-3.csv")
#The current dataset
#modelData <- selectData("dsets/android_dataset_6_4.csv")
#modelData <- selectData("dsets/android_dataset_transactions_5_19.csv")
#modelData <- selectData("../android_analysis_datasets/android_dataset_6_20_1.csv", selector=c("size", "large"))

#modelData <- selectData("../android_analysis_datasets/android_dataset_7_21.csv")
modelData <- selectData("dsets/combined_data_set_4.csv")
#modelData <- selectData("../android_analysis_datasets/android_dataset_6_29.csv")
#dataset <- modelData

#modelData <- selectData("../android_analysis_datasets/android_dataset_6_20_1.csv", selector=c("initialDate", "late"))

#modelData <- selectData("../android_analysis_datasets/android_dataset_6_29.csv", selector=c("type", "Tools"))

#data set exploratory statistics, eg, correlation statistics, marginal distributions, etc.

#ggplot2.scatterplot(data=modelData, xName='SLOC',
#                    yName='Effort',
#                    groupName="Organization")

#ggplot(modelData,aes(SLOC, Effort, color=Organization)) + 
#  geom_point() + 
#  scale_color_manual(values = c('#999999','#E69F00')) + 
#  theme(legend.position=c(0,1), legend.justification=c(0,1))


```

#load the comparative models. Each model for comparison should include two functions for evaluateion:
#1. m_fit(params, trainSet)
# params: a list of hyper parameters
# trainSet: the training dataset
#2. m_predict(model, testSet)
# model: the trained model
# testSet: the testing Set

# After create the two functions, register your model into the "models" list, as shown beblow, with a list of hyper-parameters indexed with the model name.

```{r swtiii, warning = FALSE}

#initialize models for training, testing, and evaluation. The models are put into a list with model names referencing a list of hyper-parameters, which will be passed to the model training function.

models = list()
#register the model into the models list with the hyper parameters returned from  the "trainsaction_based_model" function
transaction_models <- trainsaction_based_model(modelData)
models = append(models, transaction_models)

#models$tm3 <- trainsaction_based_model3(modelData)

#initialize the size metric based models
size_models <- size_metric_models(modelData)
#register the list of the size metric based models. 
models = append(models, size_models)

#intialize the step-wise learning model
step_model <- stepwise_linear_model(modelData, regression_cols())
models$step_lnr <- step_model

#initialize the neuralnet model
neuralnetModel = neuralnet_model(modelData, regression_cols())
models$neuralnet = neuralnetModel

#initialize the lasso regression model. having problems, need to debug
las_model = lasso_model(modelData, regression_cols())
models$lasso = las_model

#initialize the regression tree model
reg_tree_model = regression_tree_model(modelData, regression_cols())
models$reg_tree = reg_tree_model

#load the machine learning based models
#to create a model, following 3 steps:
# 1.create the model training function by rewriting this following template function
#  m_fit.MODEL_NAME <- function(MODEL_NAME,dataset){}
# 2.create the prediction function by rewriting this following template function
#  m_predict.MODEL_NAME <- function(MODEL_NAME, testData){}
# 3.add your model name into the "models"(above) variable for referencing
#  models.MODEL_NAME <- list(hyper-params...)
# examples can be found in the size_metric_based_models.R or transaction_based_model.R
  
```

```{r evaluate the effectiveness of the size metrics, warning = FALSE}
#using the entire dataset to train the models and evaluate some of the properties of the trained parameters.
#currentModels = models
#models = currentModels

#fitEval = evalFit(models, modelData, c("R2", "eta-squared"))

trainedModels <- modelTrain(models, modelData)
outputData <- modelProfile(trainedModels, modelData)
transactionData <- transaction_data_profile(modelData)
outputData <- merge(outputData, transactionData, by="row.names")

#evaluate the models for their size metrics
sizeMetricLabels <- c('SWTI', 'SWTII', 'SWTIII', 'UUCP', 'AFP', 'COSMIC', 'SLOC', "LOG_SLOC")
sizeMeasures <- data.frame(matrix(nrow=nrow(outputData), ncol=length(sizeMetricLabels)))
rownames(sizeMeasures) <- rownames(outputData)
colnames(sizeMeasures) <- sizeMetricLabels
outputData$LOG_SLOC <- log(outputData$SLOC)
sizeMeasures[,sizeMetricLabels] <- outputData[,sizeMetricLabels]
sizeMeasures <- na.omit(sizeMeasures)
effortData <- modelData[rownames(sizeMeasures), 'Effort']

#run the correlation analysis of the size metrics
sizeCor <- cor(sizeMeasures)
print(round(sizeCor, digits=2))
  
#run the correlation analysis of size metrics and project effort
effortCor <- apply(sizeMeasures, 2, function(x) {
    d <- data.frame(x=x, effortData)
    corT <- cor.test(d$x, d$Effort)
    c(corT$estimate, corT$p.value)
  })
effortCor <- t(effortCor)
colnames(effortCor) <- c("r", "p-value")
print(round(effortCor, 2))

#draw scatter plot for the project description
ggplot(outputData, aes(x=SLOC, y=Effort)) + geom_point()+theme_bw()
ggplot(outputData, aes(x=Trans, y=Effort)) + geom_point()+theme_bw()

ggplot(outputData, aes(x=SWTI, y=Effort)) + geom_point()+theme_bw()
ggplot(outputData, aes(x=SWTII, y=Effort)) + geom_point()+theme_bw()
ggplot(outputData, aes(x=SWTIII, y=Effort)) + geom_point()+theme_bw()

```
comparing the candidate models: SWTIII, UCP, COCOMO, a-priori COCOMO, using cross-validation and bootstrapping
```{r benchmark of the candidate models, warning = FALSE, fig.width=5,fig.height=4}
benchmarkResults <- modelBenchmark(models, modelData)
```

```{r evaluate goodness of fit of the models}
#evaluate goodness of fit
fitReesults <- benchmarkResults$fitResults

```

```{r evaluate the out-of-sample accuracy of the models}
#evaluate cross-validation
model_names <- benchmarkResults$model_names
accuracy_metrics <- benchmarkResults$accuracy_metrics
#plot for the cross validation results
cvResults <- benchmarkResults$cvResults
avgPreds <- cvResults[["avgPreds"]]
avgPreds <- data.frame(avgPreds)
meltAvgPreds = melt(avgPreds, id.vars="Pred")
colnames(meltAvgPreds) <- c("Pred", "Method", "Value")
model_labels <- c()
for(i in 1:length(models)){
  for(j in 1:length(accuracy_metrics)){
    model_labels = c(model_labels, names(models)[i])
  }
}

metric_labels <- c()
for(i in 1:length(models)){
  for(j in 1:length(accuracy_metrics)){
    metric_labels = c(metric_labels, accuracy_metrics[j])
  }
}


print("melt avg preds info as dots and smooth function")
ggplot(meltAvgPreds) + theme_bw() + 
		geom_point(aes(x=Pred, y=Value, group=Method,color=Method,shape=Method),size=1.5) +
		scale_shape_manual(values=c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15))+
		stat_smooth(aes(x=Pred, y=Value, group=Method,color=Method), method = lm, formula = y ~ poly(x, 10), se = FALSE)+ xlab("Relative Deviation (%)") +
		ylab("Percentage of Estimates <= x%")+ theme(legend.position="bottom")

#rank the cv results of different metric

cvAccuracyResults <- data.frame(cvResults$accuracyResults)
cvAccuracyResults$model_labels <- model_labels
cvAccuracyResults$metric_labels <- accuracy_metrics

#calculate ranking resultsb
cvRankResults <- data.frame(names(models))
names(cvRankResults)<-c("model_labels")

for (i in 1:length(accuracy_metrics)){
  g = accuracy_metrics[i]
  selectedData <- cvAccuracyResults[cvAccuracyResults$metric_labels == g,]
  selectedData <- selectedData[,-3]#delete the metric_labels
  colnames(selectedData)<-c(g, "model_labels")
  if(g == "mmre" || g == "mdmre" || g == "mae"){
    selectedData[paste("rank", i, sep = "")] <- rank(selectedData[,1], ties.method = "min")
  }else{
    selectedData[paste("rank", i, sep = "")] <- rank(-selectedData[,1], ties.method = "min")
  }
  
  cvRankResults <- merge(cvRankResults, selectedData, by = "model_labels", all=FALSE)
}

#make a total rank(rank*) base on the ranki
rank_sum <- vector(mode = "integer",length = length(models))
for (i in 1:length(models)){
  selectedData <- cvRankResults[i,]
  for(j in 1:length(accuracy_metrics)){
    rank_sum[i] <- rank_sum[i] + selectedData[,2*j+1]
  }
}
rank_sum <- rank(rank_sum, ties.method = "min")
print(rank_sum)
cvRankResults["rank*"] <- rank_sum

cvRankResults <- cvRankResults[order(cvRankResults$'rank*'),]

#change the first line as the row name
rownames(cvRankResults) = cvRankResults[,1]
cvRankResults <- cvRankResults[,-1]

print(round(cvRankResults,2))


# draw histogram base on ranking
library(ggplot2)
modelsName = rownames(cvRankResults)
p <- list()
for(i in 1:length(accuracy_metrics)){
  g = paste("rank", i, sep = "")
  selectedData <- cvRankResults[names(cvRankResults) == g]
  names(selectedData) <- c("rank");
  p[[i]] <- ggplot(selectedData, aes(x=modelsName, y=rank, fill=modelsName)) +
    geom_bar(stat="identity", colour = "black") + 
    #scale_y_discrete(expand = c(0, 0)) + 
    guides(fill = guide_legend(title = "MODEL", nrow = 1)) +
    geom_text(aes(label = rank, vjust = -0.8, hjust = 0.5)) +
    #ggtitle(accuracy_metrics[i]) +
    labs(caption=toupper(accuracy_metrics[i])) + 
    theme(plot.caption = element_text(hjust=0.5, size=rel(1)),
          #axis.line=element_blank(),
          axis.title=element_blank(), axis.text=element_blank(),axis.ticks=element_blank(), panel.background = element_blank())
}

library("cowplot")

prow <- plot_grid( p[[1]] + theme(legend.position="none"),
                   p[[2]] + theme(legend.position="none"),
                   p[[3]] + theme(legend.position="none"),
                   p[[4]] + theme(legend.position="none"),
                   p[[5]] + theme(legend.position="none"),
                   p[[6]] + theme(legend.position="none"),
                   align = 'vh',
                   hjust = -1,
                   nrow = 1
                  )
legend_b <- get_legend(p[[1]] + theme(legend.position="bottom", legend.justification="center"))
title <- ggdraw() + draw_label("Ranking Result for Cross Validation", fontface='bold')
p_cvRank <- plot_grid(title, prow, legend_b, ncol = 1, rel_heights = c(.2 , 1, .1))
p_cvRank

# draw overall ranking histogram
selectedData <- cvRankResults[names(cvRankResults) == "rank*"]
names(selectedData) <- c("rank");
p_cvAllRank <- ggplot(selectedData, aes(x=modelsName, y=rank, fill=modelsName)) +
  geom_bar(stat="identity", colour = "black", width = 0.7) + 
  #scale_y_discrete(expand = c(0, 0)) + 
  guides(fill = guide_legend(title = "MODEL", nrow = 1)) +
  geom_text(aes(label = rank, vjust = -0.8, hjust = 0.5)) +
  ggtitle("Overall Ranking Result for Cross Validation") +
  #labs(caption=toupper("Total Rank")) + 
  theme(plot.caption = element_text(hjust=0.5, size=rel(1)), legend.position = "bottom", 
        plot.title = element_text(hjust = 0.5), 
        #axis.line=element_blank(),
        axis.title=element_blank(), axis.text=element_blank(),axis.ticks=element_blank(),  panel.background = element_blank())
p_cvAllRank
```

```{r evaluate overlapping of 84% confidence intervals}
#evaluate bootstrap results
bsRet <- benchmarkResults$bsResults
#bootstrappingSE(SWTIIIModelData, otherSizeMetricsData, model3, 10000, 0.83)
bsEstimations <- bsRet[['bsEstimations']]
iterResults <- bsRet[['iterResults']]

#save as csv
#write.csv(bsEstimations, file='bsEstimations.csv', quote=F, row.names = F)
#write.csv(iterResults, file='iterResults.csv', quote=F, row.names = F)

#read from csv
#bsEstimations <- read.csv('bsEstimations.csv')
#rownames(bsEstimations) <- c('lower','mean','upper')
#iterResults <- read.csv('iterResults.csv')

# plot bootstrapping results

df <- data.frame(t(bsEstimations))
df$labels <- rownames(df)
df$model_labels <- model_labels
df$metric_labels <- metric_labels

print(metric_labels)

nonOverlappingPairs <- data.frame(matrix(ncol = 7, nrow = 0))
colnames(nonOverlappingPairs) <- c("Model1", "Model2", "Metric","Mean1", "Mean2", "84% CI1", "84% CI2")
for (i in 1:length(accuracy_metrics)){
    g = metric_labels[i]
    g_label <- toupper(g)
    selectedData <- df[df$metric_labels == g,]
    p <- ggplot(selectedData, aes(x = labels, y = mean)) + 
    geom_errorbar(aes(ymin=lower, ymax=upper), colour="black", width=.1) +
    geom_point(size=2, shape=21, fill="black") + # 21 is filled circle
    xlab('MODEL') +
    ylab(g_label) +
    scale_x_discrete(breaks=selectedData$label, labels=as.vector(selectedData$model_labels)) +
    ggtitle(paste(g_label, "- 84% Confidence Intervals", setp=""))
    print(p)
    for (j in 1:(nrow(selectedData)-1)){
      for (k in (j+1):nrow(selectedData)){
        if(selectedData[j,]$lower>selectedData[k,]$upper | selectedData[j,]$upper<selectedData[k,]$lower){
          #selectedData[j,] and selectedData[k,] non-overlap
          nonOverlap <- data.frame(
            selectedData[j,]$model_labels,
            selectedData[k,]$model_labels,
            g,
            round(selectedData[j,]$mean, 3),
            round(selectedData[k,]$mean, 3),
            paste0("[", as.character(round(selectedData[j,]$lower, 3)), ", ", as.character(round(selectedData[j,]$upper, 3)), "]"),
            paste0("[", as.character(round(selectedData[k,]$lower, 3)), ", ", as.character(round(selectedData[k,]$upper, 3)), "]")
            )
          colnames(nonOverlap) <- c("Model1", "Model2", "Metric","Mean1", "Mean2", "84% CI1", "84% CI2")
          nonOverlappingPairs <- rbind(nonOverlappingPairs, nonOverlap)
        }
      }
    }
}

nonOverlappingPairs = nonOverlappingPairs[which(nonOverlappingPairs$Model1 %in% c("tm3", "tm2", "tm1") | nonOverlappingPairs$Model2 %in% c("tm3", "tm2", "tm1")),]

print(nonOverlappingPairs)


for (i in 1:length(accuracy_metrics)){
    g = metric_labels[i]
    g_label <- toupper(g)
    selectedData <- df[df$metric_labels == g,]
    p <- ggplot(selectedData, aes(x = labels, y = mean)) + 
    geom_errorbar(aes(ymin=lower, ymax=upper), colour="black", width=.1) +
    geom_point(size=2, shape=21, fill="black") + # 21 is filled circle
    xlab('MODEL') +
    ylab(g_label) +
    scale_x_discrete(breaks=selectedData$label, labels=as.vector(selectedData$model_labels)) +
    ggtitle(paste(g_label, "- 84% Confidence Intervals", setp=""))+
    theme_bw()
    print(p)
}

# draw a partially ordered graph based on non-overlapping pairs


# for (i in 1:length(metric_labels)){
#     g = metric_labels[i]
#     selectedData <- df[df$metric_labels == g,]
#     p <- ggplot(selectedData, aes(x = labels, y = mean, ymin = lower, ymax = upper, fill = metric_labels)) +
#     geom_crossbar(width = 0.5, position = "dodge") +
#     #coord_flip() +
#     scale_x_discrete(breaks=selectedData$label, labels=as.vector(selectedData$model_labels)) +
#     xlab('model') +
#     ylab(g) +
#     ggtitle(g)
#     print(p)
# }
```

```{r evaluate the p-values under family-wise control}

foldResults <- cvResults$foldResults

sig_bs <- familywiseHypoTest(iterationResults=iterResults, accuracy_metrics, model_names, "boot")


round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))

  df[,nums] <- round(df[,nums], digits = digits)

  (df)
}

sig_bs_f = sig_bs[which(sig_bs$BH_p_value < 0.05),]
sig_bs_f = sig_bs_f[which(sig_bs_f$metric %in% c("mmre", "mdmre", "pred25", "mae")),]
sig_bs_f = sig_bs_f[which(sig_bs_f$model1 %in% c("tm3") | sig_bs_f$model2 %in% c("tm3")),]
sig_bs_f = sig_bs_f[order(sig_bs_f$bonferroni_p_value),]
sig_bs_f = round_df(sig_bs_f, 2)
print(sig_bs_f)


# Using the "sig_bs" results, create a graph to represent the direct graph for the models.
library(igraph)
for(metric_i in 1:length(accuracy_metrics)){
  selectedData <- sig_bs[sig_bs$metric == metric_labels[metric_i],]
  m <- matrix(0, nrow = length(models), ncol = length(models), byrow = FALSE)
  colnames(m) <- names(models)
  rownames(m) <- names(models)
  for(i in 1:nrow(selectedData)){
    if(selectedData$BH_p_value[i] < 0.05){
    if(selectedData$direction[i] == "+"){
      m[as.character(selectedData$model1[i]), as.character(selectedData$model2[i])] = round(selectedData$bonferroni_p_value[i], 3)
    }else if(selectedData$direction[i] == "-"){
      m[as.character(selectedData$model2[i]), as.character(selectedData$model1[i])] = round(selectedData$bonferroni_p_value[i], 3)
    }
    }
  }
  
  edge_val <- c() 
  # if A -> B -> C, remove edge A -> C
  for(i in 1:length(models)){
    for(j in 1:length(models)){
      if(m[i,j] != 0){
        edge_val <- c(edge_val, m[i,j]) 
        for(k in 1:length(models)){
          if(m[j,k] != 0)
            m[i,k] = 0
        }
      }
    }
  }
  
  #plot the directed graph
  model_mean <- matrix(0, nrow = length(models), byrow = FALSE)
  rownames(model_mean) <- names(models)
  colnames(model_mean) <- "mean"
  for(i in 1:nrow(selectedData)){
    model_mean[which(rownames(model_mean) == selectedData[i,]$model1)] = round(selectedData[i,]$model1_mean, 3)
    model_mean[which(rownames(model_mean) == selectedData[i,]$model2)] = round(selectedData[i,]$model2_mean, 3)
  }

  net=graph.adjacency(m,mode="directed",weighted=TRUE,diag=FALSE)
  
  plot.igraph(net,vertex.label=paste(V(net)$name, model_mean[which(rownames(model_mean) == V(net)$name)], sep = " : "), layout=layout.fruchterman.reingold,
              vertex.color="white", vertex.label.color="black", vertex.size=25,
              edge.color="black", edge.label = edge_val, edge.width=3, edge.arrow.size=0.5, edge.arrow.width=1.2)
  
  title(main = metric_labels[metric_i])
}


# filter for 

```

```{r stratified analysis, warning = FALSE}
projectCategories <- as.matrix(read.csv("./project_categorization.csv"))
print(projectCategories)
nCategories <- nrow(projectCategories)
benchmarkLabels <- paste("b", seq(1, nCategories, by=1), sep="")
categorizedBenchmarkResults = list()

for(i in 1:nCategories){
  #print(projectCategories[i, ])
  categorizedDataset <- selectData("../android_analysis_datasets/android_dataset_6_29.csv", selector=projectCategories[i,])

  #categorizedDataset <- selectData("../android_analysis_datasets/android_dataset_6_29.csv", selector=c("initialDate","early"))
  
  #categorizedDataset <- selectData("../android_analysis_datasets/android_dataset_6_29.csv", selector=c("type","Productivity"))
  
  print(categorizedDataset)
  categorizedBenchmarkResults[[benchmarkLabels[i]]] <- modelBenchmark(models, categorizedDataset)

}


#9 categorized benchmarking results are produced
#1-3 are the projects of sizes: small, medium, and large
#4-6 are the projects of initialDate: early, normal, and late
#7-10 are the projects of different types: Game, Tools, Entertainment, Productivity.


```