---
title: "Transaction Weight Calibration Visualized"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("utils/feature_selection.R")
source("utils/data_selection.R")
source("utils/model_funcs.R")
source("accuracy_confidence_evaluation.R")
source("transaction_based_model.R")
source("size_metric_based_models.R")
source("neuralnet_model.R")
source("stepwise_linear_model.R")
source("lasso_regression_model.R")
source("regression_tree_model.R")
source('familywiseHypoTest.R')
library(jsonlite)
library(reshape)
library(tidyverse)
library(fitdistrplus)
library(egg)
library(gridExtra)
library(plyr)
library(lsr)
library("Hmisc")
require(MASS)
library("grid")
library("ggplotify")
library("cowplot")
```
Combined Data Effort Values
```{r descriptive statistics, fig.width=5,fig.height=2.5}
#The previous dataset
#modelData <- selectData("dsets/modelEvaluations-1-3.csv")
#The current dataset
#modelData <- selectData("dsets/android_dataset_6_4.csv")
#modelData <- selectData("dsets/android_dataset_transactions_5_19.csv")
#modelData <- selectData("../android_analysis_datasets/android_dataset_6_20_1.csv", selector=c("size", "large"))

#modelData <- selectData("../android_analysis_datasets/android_dataset_7_21.csv")
#outputDir = "."
#outputDir = "./res/9-5-6-models-34-data-points"
#outputDir = "./res/8-28-6-models-34-data-points"
#outputDir = "./res/8-28-6-models-bootstrap-100-34-data-points"
outputDir = "./res/9-1-6-models-577-61-data-points"
#outputDir = "./res/9-5-8-models"
#outputDir = "./res/9-15-8-models"
#outputDir = "./res/10-1-8-models"
#outputDir = "./res/10-1-8-models"
print(outputDir)
#outputDir = "./res/8-27-8-models"
#outputDir = "./res/8-27-6-models"
#dataset <- read.csv("dsets/combined_data_set_4.csv")
#dataset <- read.csv("dsets/combined_data_set_4_rufus.csv")
#dataset <- read.csv("dsets/combined_data_set_8_22.csv")
#dataset <- read.csv("dsets/combined_data_set_8_23.csv")
#dataset <- read.csv("dsets/combined_data_set_8_26.csv")
#dataset <- read.csv("dsets/combined_data_set_8_28.csv") #current
#dataset <- read.csv("dsets/combined_data_set_4_1.csv")
#dataset <- read.csv("dsets/modelEvaluations-5-4.csv")
#dataset <- read.csv("res/10-1-8-models/combined_data_set_10_1.csv")
dataset <- read.csv("./res/9-1-6-models-577-61-data-points/modelEvaluations-5-4.csv")
modelData <- selectData(dataset)
#modelData <- selectData("../android_analysis_datasets/android_dataset_6_29.csv")
#dataset <- modelData

#modelData <- selectData("../android_analysis_datasets/android_dataset_6_20_1.csv", selector=c("initialDate", "late"))

#modelData <- selectData("../android_analysis_datasets/android_dataset_6_29.csv", selector=c("type", "Tools"))

#data set exploratory statistics, eg, correlation statistics, marginal distributions, etc.

#ggplot2.scatterplot(data=modelData, xName='SLOC',
#                    yName='Effort',
#                    groupName="Organization")

#ggplot(modelData,aes(SLOC, Effort, color=Organization)) + 
#  geom_point() + 
#  scale_color_manual(values = c('#999999','#E69F00')) + 
#  theme(legend.position=c(0,1), legend.justification=c(0,1))

#datasetUCP <- read.csv("./dsets/parallel_agile_10_27.csv")
datasetUCP <- read.csv("./res/9-1-6-models-577-61-data-points/parallel_agile_10_27.csv")
cor(datasetUCP$EUCP_Size, datasetUCP$Actual_PH)
cor(datasetUCP$EXUCP_Size, datasetUCP$Actual_PH)
cor(datasetUCP$DUCP_Size, datasetUCP$Actual_PH)

cor.test(datasetUCP$EUCP_Size, datasetUCP$Actual_PH) 
cor.test(datasetUCP$EXUCP_Size, datasetUCP$Actual_PH)
cor.test(datasetUCP$DUCP_Size, datasetUCP$Actual_PH)

lm1 = lm(Actual_PH ~ EUCP_Size, data=datasetUCP)
summary(lm1)$r.squared 
print(summary(lm1))

lm2 = lm(Actual_PH ~ EXUCP_Size, data=datasetUCP)
summary(lm2)$r.squared 
print(summary(lm2))

lm3 = lm(Actual_PH ~ DUCP_Size, data=datasetUCP)
summary(lm3)$r.squared
print(summary(lm3))

hist(transactionData1$combined$TL)
hist(transactionData1$combined$DETs)
hist(transactionData1$combined$TD)
```

#load the comparative models. Each model for comparison should include two functions for evaluateion:
#1. m_fit(params, trainSet)
# params: a list of hyper parameters
# trainSet: the training dataset
#2. m_predict(model, testSet)
# model: the trained model
# testSet: the testing Set

# After create the two functions, register your model into the "models" list, as shown beblow, with a list of hyper-parameters indexed with the model name.

```{r swtiii, warning = FALSE}

#initialize models for training, testing, and evaluation. The models are put into a list with model names referencing a list of hyper-parameters, which will be passed to the model training function.
#models = models3
#models3 = models
models = list()
#models1 = models
#register the model into the models list with the hyper parameters returned from  the "trainsaction_based_model" function
#transaction_models1 <- transaction_models
transaction_models <- trainsaction_based_model(modelData)
#transaction_models_1 <- transaction_models
models = append(models, transaction_models)

print(outputDir)

#profile iteration data
iterationData0 <- profileIterationData(transaction_models$tm1$SWTIresults)
write.csv(round(iterationData0$trainedModels[[1]], digits=2), paste(outputDir, 'parameters_swtI.csv', sep="/"))

iterationData <- profileIterationData(transaction_models$tm3$SWTIIIresults)
print(iterationData$lcuts)
write.csv(iterationData$lcuts, paste(outputDir, 'cut_points_swtIII.csv', sep="/"))
print(as.matrix(iterationData$laccuracy))
write.csv(as.matrix(iterationData$laccuracy), paste(outputDir, 'iteration_results_accuracy_swtIII.csv', sep="/"))
print(iterationData$trainedModels[[3]])
write.csv(round(iterationData$trainedModels[[3]], digits=2), paste(outputDir, 'parameters_swtIII.csv', sep="/"))

iterationData1 <- profileIterationData(transaction_models$tm2$SWTIIresults)
print(as.matrix(iterationData1$laccuracy))
write.csv(as.matrix(iterationData1$laccuracy), paste(outputDir, 'iteration_results_accuracy_swtII.csv', sep="/"))
print(iterationData1$trainedModels[[4]])
write.csv(round(iterationData1$trainedModels[[4]], digits=2), paste(outputDir, 'parameters_swtII.csv', sep="/"))
#models$tm3 <- trainsaction_based_model3(modelData)

#initialize the size metric based models
size_models <- size_metric_models(modelData)
#register the list of the size metric based models. 
models = append(models, size_models)
#models$cosmic = size_models$cosmic
#models$fp = size_models$fp

#intialize the step-wise learning model
step_model <- stepwise_linear_model(modelData, regression_cols())
models$step_lnr <- step_model

#initialize the neuralnet model
neuralnetModel = neuralnet_model(modelData, regression_cols())
models$neuralnet = neuralnetModel

#initialize the lasso regression model. having problems, need to debug
las_model = lasso_model(modelData, regression_cols())
models$lasso = las_model

#initialize the regression tree model
reg_tree_model = regression_tree_model(modelData, regression_cols())
models$reg_tree = reg_tree_model

#models backup
#models1 = models

#load the machine learning based models
#to create a model, following 3 steps:
# 1.create the model training function by rewriting this following template function
#  m_fit.MODEL_NAME <- function(MODEL_NAME,dataset){}
# 2.create the prediction function by rewriting this following template function
#  m_predict.MODEL_NAME <- function(MODEL_NAME, testData){}
# 3.add your model name into the "models"(above) variable for referencing
#  models.MODEL_NAME <- list(hyper-params...)
# examples can be found in the size_metric_based_models.R or transaction_based_model.R
  
```

```{r evaluate the effectiveness of the size metrics, warning = FALSE}
#using the entire dataset to train the models and evaluate some of the properties of the trained parameters.
#currentModels = models
#models = currentModels

#fitEval = evalFit(models, modelData, c("R2", "eta-squared"))
#tm3 <- models$tm3
#models$tm2 <- tm3
trainedModels <- modelTrain(models, modelData)
outputData <- modelProfile(trainedModels, modelData)
transactionData <- transaction_data_profile(modelData)
outputData <- merge(outputData, transactionData, by="row.names")
rownames(outputData) <- outputData$Row.names
outputData$Row.names <- NULL
write.csv(round(outputData, digits=2), paste(outputDir, "output_data.csv", sep="/"))
outputData1 <- outputData
effortData <- modelData[rownames(sizeMeasures), 'Effort']

outputCSV <- read.csv("./res/9-5-8-models/output_csv.csv")
outputData <- outputCSV
rownames(outputData) <- outputData$Proj
effortData <- outputCSV$Effort
sizeMeasures = outputData

cor(log(sizeMeasures$SLOC), log(effortData))
sizeMeasures$LOG_EFFORT = log(effortData)

log_sloc.lm = lm(LOG_EFFORT ~ LOG_SLOC, data=sizeMeasures)
summary(log_sloc.lm)$r.squared
print(summary(log_sloc.lm))

sloc.lm = lm(Effort ~ SLOC, data=outputData)
summary(sloc.lm)$r.squared 
print(summary(sloc.lm))

cosmic.lm = lm(Effort ~ COSMIC, data=outputData)
summary(cosmic.lm)$r.squared
print(summary(cosmic.lm))

swtii.lm = lm(Effort ~ SWTII, data=outputData)
summary(swtii.lm)$r.squared
print(summary(swtii.lm))

swtiii.lm = lm(Effort ~ SWTIII, data=outputData)
summary(swtiii.lm)$r.squared 
print(summary(swtiii.lm))

swti.lm = lm(Effort ~ SWTI, data=outputData)
summary(swti.lm)$r.squared
print(summary(swti.lm))

ifpug.lm = lm(Effort ~ AFP, data=outputData)
summary(ifpug.lm)$r.squared 
print(summary(ifpug.lm))

uucp.lm = lm(Effort ~ UUCP, data=outputData)
summary(uucp.lm)$r.squared 
print(summary(uucp.lm))

#evaluate the models for their size metrics
sizeMetricLabels <- c('SWTI', 'SWTII', 'SWTIII', 'UUCP', 'AFP', 'COSMIC', 'SLOC', "LOG_SLOC")
#sizeMetricLabels <- c('SWTIII', 'UUCP', 'AFP', 'COSMIC', 'SLOC', "LOG_SLOC")
#sizeMetricLabels <- c('SWTI', 'UUCP', 'AFP', 'COSMIC', 'SLOC', "LOG_SLOC")
sizeMeasures <- data.frame(matrix(nrow=nrow(outputData), ncol=length(sizeMetricLabels)))
rownames(sizeMeasures) <- rownames(outputData)
colnames(sizeMeasures) <- sizeMetricLabels
sizeMeasures[,sizeMetricLabels] <- outputData[,sizeMetricLabels]
sizeMeasures <- na.omit(sizeMeasures)
sizeMeasures <- sizeMeasures[!is.infinite(rowSums(sizeMeasures)),]

#run the correlation analysis of the size metrics
sizeCor <- rcorr(as.matrix(sizeMeasures))
print(round(sizeCor$r, digits=2))
print(round(sizeCor$P, digits=3))
write.csv(round(sizeCor$r, digits=2), paste(outputDir, "size_metric_cor_matrix.csv", sep="/"))
write.csv(round(sizeCor$P, digits=3), paste(outputDir, "size_metric_cor_matrix_p.csv", sep="/"))

#run the correlation analysis of size metrics and project effort
effortCor <- apply(sizeMeasures, 2, function(x) {
    d <- data.frame(x=x, Effort=effortData)
    corT <- cor.test(d$x, d$Effort)
    c(corT$estimate, corT$p.value)
})


effortCor <- t(effortCor)
colnames(effortCor) <- c("r", "p-value")
    effortCorRank <- as.data.frame(effortCor)
effortCorRank["Rank"] <- rank(-effortCorRank[,"r"], ties.method = "min")
effortCorRank <- effortCorRank[order(effortCorRank$Rank),]
print(round(effortCorRank, 2))
#print(cor(sizeMeasures$LOG_SLOC, log(effortData)))
write.csv(round(effortCorRank, 2), paste(outputDir, "effort_cor_rank.csv", sep="/"))

print(outputDir)
#draw scatter plot for the project description
ggplot(outputData, aes(x=SLOC, y=Effort)) + geom_point()+theme_bw()
ggplot(outputData, aes(x=LOG_SLOC, y=Effort)) + geom_point()+theme_bw()
ggplot(outputData, aes(x=Trans, y=Effort)) + geom_point()+theme_bw()
ggplot(outputData, aes(x=SWTI, y=Effort)) + geom_point()+theme_bw()
#ggplot(outputData, aes(x=SWTII, y=Effort)) + geom_point()+theme_bw()
#ggplot(outputData, aes(x=SWTIII, y=Effort)) + geom_point()+theme_bw()

print(models$tm2$cuts)
print(models$tm3$cuts)

```
Benchmark the candidate models: SWTIII, UCP, COCOMO, a-priori COCOMO, using cross-validation and bootstrapping
```{r benchmark of the candidate models, warning = FALSE, fig.width=5,fig.height=4}
benchmarkResults <- modelBenchmark(models, modelData)
benchmarkResultsTest4 = benchmarkResults
#benchmarkResultsTest3 = benchmarkResults
#benchmarkResultsTest2 = benchmarkResults
#benchmarkResultsTest1 = benchmarkResults
#benchmarkResults = benchmarkResultsTest1

#tm2 = trainedModels$tm2
#save(tm2, file="models/swtii.Rdata")
#tm3 = trainedModels$tm3
#save(tm3, file="models/swtiii.Rdata")
#ucp = trainedModels$ucp
#save(ucp, file="models/ucp.Rdata")

#update the benchmark results for specific models
#dataset1 <- read.csv("dsets/combined_data_set_8_27.csv")
#modelData1 <- selectData(dataset1)
models2 = list()
models2$cosmic = size_models$cosmic
#models2$ln_sloc = size_models$ln_sloc
#models2$cosmic = models$cosmic
#models2$ln_sloc = models$ln_sloc
#models2$step_lnr = models$step_lnr
models2$neuralnet = models$neuralnet
#models2$lasso = models$lasso
#models2$reg_tree= models$reg_tree
#models2$tm3 = transaction_models$tm3
models2$step_lnr <- step_model
benchmarkResultsTemp <- modelBenchmark(models2, modelData)
#benchmarkResults <- updateBenchmarkResults(benchmarkResults, benchmarkResultsTemp)

#iterR2 <- benchmarkResultsTemp$bsResults$iterResults
#print(iterR2)
benchmarkResults <- modelBenchmarkIndividual(models2, modelData, benchmarkResultsTest3)

#bechmark backup
#benchmarkResults1 <- benchmarkResults

#model_names <- benchmarkResults$model_names

#test 1
#model_names <- c("ucp", "fp", "cosmic", "sloc", "ln_sloc")
#model_texts <- c("UCP", "IFPUG", "COSMIC", "SLOC", "LOG_SLOC")
#model_estimator <- c("LSR", "LSR", "LSR", "LSR", "LSR")

#test 2
model_names <- c("neuralnet", "lasso", "reg_tree", "tm1", "ucp", "fp", "cosmic", "sloc", "ln_sloc", "step_lnr")
model_texts <- c("NEURAL_NET", "LASSO", "REG_TREE", "TRAN", "UCP", "IFPUG", "COSMIC", "SLOC", "LOG_SLOC", "STEP_REG")
model_estimator <- c("ANN", "LASSO", "REG TREE", "LSR", "LSR", "LSR", "LSR", "LSR", "LSR", "STEP")

#model_names <- c("ucp", "fp", "cosmic", "sloc", "ln_sloc")
#model_texts <- c("UCP", "IFPUG", "COSMIC", "SLOC", "LOG_SLOC")
#model_estimator <- c("LSR", "LSR", "LSR", "LSR", "LSR")

#test 3
model_names <- c("tm3", "ucp", "fp", "cosmic", "sloc", "ln_sloc")
model_texts <- c("TRAN", "UCP", "IFPUG", "COSMIC", "SLOC", "LOG_SLOC")
model_estimator <- c("LSR", "LSR", "LSR", "LSR", "LSR", "LSR")

#test 4
#model_names <- c("ucp", "fp", "cosmic", "sloc", "ln_sloc", "step_lnr")
#model_texts <- c("UCP", "IFPUG", "COSMIC", "SLOC", "LOG_SLOC", "STEP_REG")
#model_estimator <- c("LSR", "LSR", "LSR", "LSR", "LSR", "STEP")

#test 5
model_names <- c("tm1","tm2","tm3", "ucp", "fp", "cosmic", "sloc", "ln_sloc")
model_texts <- c("SWTII","SWTIII","SWTI", "UCP", "IFPUG", "COSMIC", "SLOC", "LOG_SLOC")
model_estimator <- c("LSR","LSR","LSR", "LSR", "LSR", "LSR", "LSR", "LSR")

#test 6
model_names <- c("neuralnet", "reg_tree", "tm1", "step_lnr")
model_texts <- c("NEURAL_NET", "REG_TREE", "TRAN", "STEP_REG")
model_estimator <- c("ANN", "REG TREE", "LSR", "STEP")

#test 7
model_names <- c("tm1","tm2","tm3", "fp")
model_texts <- c("SWTII","SWTIII","SWTI", "IFPUG")
model_estimator <- c("LSR","LSR","LSR", "LSR")

print(outputDir)
model_mapping <- data.frame(model_names=model_names, model_texts=model_texts, model_estimator=model_estimator)

#accuracy_metrics <- c('mmre','pred15','pred25','pred50', 'mdmre', 'mae', 'predRange')
#accuracy_metric_texts <- c('MMRE','PRED15','PRED25','PRED50', 'MDMRE', 'MAE', 'PREDRANGE')
accuracy_metrics <- c('mmre', 'pred25', 'mdmre', 'mae')
accuracy_metric_texts <- c('MMRE', 'PRED25', 'MDMRE', 'MAE')
accuracy_mapping <- data.frame(accuracy_metrics = accuracy_metrics, accuracy_metric_texts=accuracy_metric_texts)
#accuracy_metrics <- benchmarkResults$accuracy_metric
#accuracy_metrics <- accuracy_metrics[!accuracy_metrics %in% c("pred15", "pred50")]
goodness_fit_metrics = benchmarkResults$goodness_fit_metrics
fitResults <- benchmarkResults$fitResults
cvResults <- benchmarkResults$cvResults
foldResults <- cvResults$foldResults
bsRet <- benchmarkResults$bsResults
bsEstimations <- bsRet[['bsEstimations']]
iterResults <- bsRet[['iterResults']]

#neuralnet <- load_model(c("neuralnet"))

model_labels <- c()
for(i in 1:length(model_names)){
  for(j in 1:length(accuracy_metrics)){
    model_labels = c(model_labels, model_names[i])
  }
}
print(model_labels)

metric_labels <- c()
for(i in 1:length(model_names)){
  for(j in 1:length(accuracy_metrics)){
    metric_labels = c(metric_labels, accuracy_metrics[j])
  }
}

accuracy_labels <- paste(model_labels, metric_labels, sep="_")
model_mapping_2 <- data.frame(model_labels = model_labels, metric_labels=metric_labels, accuracy_labels = accuracy_labels)
print(accuracy_labels)

```

```{r evaluate goodness of fit of the models}
#evaluate goodness of fit
#print(outputDir)
goodnessRankResults = data.frame(model_labels = model_names)
goodnessRankResults <- merge(goodnessRankResults, model_mapping, by.x = "model_labels", by.y="model_names", all=FALSE)

for (i in 1:length(goodness_fit_metrics)){
  g = goodness_fit_metrics[i]
  selectData = data.frame(matrix(ncol=0, nrow=length(model_names)))
  selectData$model_labels <- model_names
  rownames(selectData) = selectData$model_labels
  selectData[, g] <- c()
  for(j in 1:length(model_names)){
  m = fitResults[[model_names[j]]]
  m_name = model_names[j]
  selectData[m_name, g] <- m[[g]]
  }
  selectData[, g] = round(selectData[, g],2)
  goodnessRankResults <- merge(goodnessRankResults, selectData, by = "model_labels", all=FALSE)
}


goodnessRankResults["Rank"] <- rank(-goodnessRankResults[,"R2"], ties.method = "min")
goodnessRankResults <- goodnessRankResults[order(goodnessRankResults$Rank),]
print(goodnessRankResults)
write.csv(goodnessRankResults, paste(outputDir, "goodness_rank_results.csv", sep="/"))
```

```{r evaluate the out-of-sample accuracy of the models}
#evaluate cross-validation and plot the cross validation results for pred(.01)- pred(0.50)

avgPreds <- cvResults[["avgPreds"]]
avgPreds <- data.frame(avgPreds)
avgPreds <- avgPreds[,names(avgPreds) %in% c(model_names, "Pred")]
names(avgPreds) <- model_mapping$model_texts[match(names(avgPreds), model_mapping$model_names)]
names(avgPreds)[1] = c("Pred")

print(outputDir)

#apply new labels
#colnames(avgPreds) <- c("Pred", "SWT", "UUCP", "AFP", "COSMIC", "SLOC", "LOG SLOC")
#colnames(avgPreds) <- c("Pred", "SWT-I", "SWT-II", "SWT-III", "UUCP", "AFP", "COSMIC", "SLOC", "LOG SLOC")
#colnames(avgPreds) <- c("Pred", "SWT-I", "SWT-II", "SWT-III", "UUCP", "AFP", "COSMIC", "SLOC", "LOG SLOC")
#colnames(avgPreds) <- c("Pred", "NEURAL_NET", "LASSO", "REG_TREE", "TRAN", "UCP", "IFPUG", "COSMIC", "SLOC", "LOG_SLOC", "STEP_REG")
meltAvgPreds = melt(avgPreds, id.vars="Pred")
colnames(meltAvgPreds) <- c("Pred", "Method", "Value")
print("melt avg preds info as dots and smooth function")
avg_pred_plot = ggplot(meltAvgPreds) + theme_bw() + 
		geom_point(aes(x=Pred, y=Value, group=Method,color=Method,shape=Method),size=1.5) +
		scale_shape_manual(values=seq(from=1, to = length(model_names), by =1))+
		stat_smooth(aes(x=Pred, y=Value, group=Method,color=Method), method = lm, formula = y ~ poly(x, 10), se = FALSE)+ xlab("Relative Deviation (%)") +
		ylab("Percentage of Estimates <= x%")+ theme(legend.position="bottom")
print(avg_pred_plot)
ggsave(paste(outputDir, "avg_pred_plot.png", sep="/"), width=5, height=3.5)

#rank the cv results of different metric

cvAccuracyResults <- data.frame(cvResults$accuracyResults)
cvAccuracyResults$label <- rownames(cvAccuracyResults)
#cvAccuracyResults <- cvAccuracyResults[- grep("predRange", cvAccuracyResults$label),]
cvAccuracyResults <- cvAccuracyResults[cvAccuracyResults$label %in% accuracy_labels,]
cvAccuracyResults <- merge(cvAccuracyResults, model_mapping_2, by.x = "label", by.y="accuracy_labels", all=FALSE)
cvAccuracyResults$label <- NULL

#calculate ranking results
cvRankResults <- data.frame(model_names)
names(cvRankResults)<-c("model_labels")

for (i in 1:length(accuracy_metrics)){
  g = accuracy_metrics[i]
  selectedData <- cvAccuracyResults[cvAccuracyResults$metric_labels == g,]
  selectedData <- selectedData[,-3]#delete the metric_labels
  colnames(selectedData)<-c(g, "model_labels")
  if(g == "mmre" || g == "mdmre" || g == "mae"){
    selectedData[paste("rank", i, sep = "")] <- rank(selectedData[,1], ties.method = "min")
  }else{
    selectedData[paste("rank", i, sep = "")] <- rank(-selectedData[,1], ties.method = "min")
  }
  
  cvRankResults <- merge(cvRankResults, selectedData, by = "model_labels", all=FALSE)
}

#make a total rank(rank*) base on the ranks
rank_sum <- vector(mode = "integer",length = length(model_names))
for (i in 1:length(model_names)){
  selectedData <- cvRankResults[i,]
  for(j in 1:length(accuracy_metrics)){
    rank_sum[i] <- rank_sum[i] + selectedData[,2*j+1]
  }
}
rank_sum <- rank(rank_sum, ties.method = "min")
print(rank_sum)
cvRankResults["rank*"] <- rank_sum


#change the first line as the row name
#cvRankResults <- merge(cvRankResults, model_mapping, by.x = "model_labels", by.y="model_names", all=FALSE)
#rownames(cvRankResults) = cvRankResults$model_texts
#cvRankResults$model_labels = NULL
#cvRankResults$model_estimator = NULL
#cvRankResults$model_texts = NULL

rownames(cvRankResults) <- model_mapping$model_texts[match(cvRankResults$model_labels, model_mapping$model_names)]
cvRankResults$model_labels = NULL

cvRankResults <- cvRankResults[order(cvRankResults$'rank*'),]

print(round(cvRankResults,2))

write.csv(round(cvRankResults,2), paste(outputDir, "cv_rank_results.csv", sep="/"))

# draw histogram base on ranking
library(ggplot2)
p <- list()
for(i in 1:length(accuracy_metrics)){
  g = paste("rank", i, sep = "")
  selectedData <- cvRankResults[names(cvRankResults) == g]
  names(selectedData) <- c("rank");
  p[[i]] <- ggplot(selectedData, aes(x=rownames(cvRankResults), y=rank, fill=rownames(cvRankResults))) +
    geom_bar(stat="identity", colour = "black") + 
    #scale_y_discrete(expand = c(0, 0)) + 
    guides(fill = guide_legend(title = "MODEL", nrow = 2)) +
    geom_text(aes(label = rank, vjust = -0.3, hjust = 0.5)) +
    #ggtitle(accuracy_metrics[i]) +
    labs(caption=toupper(accuracy_metrics[i])) + 
    theme(plot.caption = element_text(hjust=0.5, vjust = 2.5, size=rel(1)),
          #axis.line=element_blank(),
          axis.title=element_blank(), axis.text=element_blank(),axis.ticks=element_blank(), panel.background = element_blank())
}

prow <- plot_grid( p[[1]] + theme(legend.position="none"),
                   p[[2]] + theme(legend.position="none"),
                   p[[3]] + theme(legend.position="none"),
                   p[[4]] + theme(legend.position="none"),
                   align = 'vh',
                   hjust = 0,
                   nrow = 1
                  )
legend_b <- get_legend(p[[1]] + theme(legend.position="bottom", legend.justification="center"))
title <- ggdraw() + draw_label("Ranking Result for Cross Validation", fontface='bold')
p_cvRank <- plot_grid(title, prow, legend_b, ncol = 1, rel_heights = c(.2 , 1, .1))
p_cvRank

# draw overall ranking histogram
selectedData <- cvRankResults[names(cvRankResults) == "rank*"]
names(selectedData) <- c("rank");
p_cvAllRank <- ggplot(selectedData, aes(x=rownames(selectedData), y=rank, fill=rownames(selectedData))) +
  geom_bar(stat="identity", colour = "black", width = 0.7) + 
  #scale_y_discrete(expand = c(0, 0)) + 
  guides(fill = guide_legend(title = "MODEL", nrow = 2)) +
  geom_text(aes(label = rank, vjust = -0.4, hjust = 0.5)) +
  ggtitle("Overall Ranking Result for Cross Validation") +
  #labs(caption=toupper("Total Rank")) + 
  theme(plot.caption = element_text(hjust=0.5, size=rel(0.5)), legend.position = "bottom",legend.text=element_text(size=10), 
        plot.title = element_text(hjust = 0.5), 
        #axis.line=element_blank(),
        axis.title=element_blank(), axis.text=element_blank(),axis.ticks=element_blank(),  panel.background = element_blank())
p_cvAllRank

```

```{r evaluate overlapping of 84% confidence intervals}
#evaluate bootstrap results
#bootstrappingSE(SWTIIIModelData, otherSizeMetricsData, model3, 10000, 0.83)

#save as csv
#write.csv(bsEstimations, file='bsEstimations.csv', quote=F, row.names = F)
#write.csv(iterResults, file='iterResults.csv', quote=F, row.names = F)

#read from csv
#bsEstimations <- read.csv('bsEstimations.csv')
#rownames(bsEstimations) <- c('lower','mean','upper')
#iterResults <- read.csv('iterResults.csv')

# plot bootstrapping results

df <- data.frame(t(bsEstimations))
df$label <- rownames(df)
#df <- df[- grep("predRange", df$labels),]
#df <- df[- grep("pred15", df$labels),]
#df <- df[- grep("pred50", df$labels),]
#df <- df[- grep("tm2", df$labels),]
#df <- df[- grep("tm3", df$labels),]
df <- df[df$label %in% accuracy_labels,]
df <- merge(df, model_mapping_2, by.x = "label", by.y="accuracy_labels", all=FALSE)

nonOverlappingPairs <- data.frame(matrix(ncol = 8, nrow = 0))
overlappingPairAttrs <- c("model1", "model2", "metric", "direction", "mean1", "mean2", "84% CI1", "84% CI2")
colnames(nonOverlappingPairs) <- overlappingPairAttrs
for (i in 1:length(accuracy_metrics)){
    g = metric_labels[i]
    selectedData <- df[df$metric_labels == g,]
    for (j in 1:(nrow(selectedData)-1)){
      for (k in (j+1):nrow(selectedData)){
        if(selectedData[j,]$lower>selectedData[k,]$upper | selectedData[j,]$upper<selectedData[k,]$lower){
          #selectedData[j,] and selectedData[k,] non-overlap
          direction = "="
          if(selectedData[j,]$mean > selectedData[k,]$mean){
            direction = "+"
          }
          else if(selectedData[j,]$mean < selectedData[k,]$mean){
            direction = "-"
          }
          
          if(selectedData[j,]$metric %in% c("mae", "mdmre", "mmre")){
            if(direction == "+"){
              direction = "-"
            }
            else if(direction == "-"){
              direction = "+"
            }
          }
          nonOverlap <- data.frame(
            selectedData[j,]$model_labels,
            selectedData[k,]$model_labels,
            g,
            direction,
            round(selectedData[j,]$mean, 3),
            round(selectedData[k,]$mean, 3),
            paste0("[", as.character(round(selectedData[j,]$lower, 3)), ", ", as.character(round(selectedData[j,]$upper, 3)), "]"),
            paste0("[", as.character(round(selectedData[k,]$lower, 3)), ", ", as.character(round(selectedData[k,]$upper, 3)), "]")
            )
          colnames(nonOverlap) <- overlappingPairAttrs
          nonOverlappingPairs <- rbind(nonOverlappingPairs, nonOverlap)
        }
      }
    }
}

print(nonOverlappingPairs)
write.csv(nonOverlappingPairs, paste(outputDir, 'nonOverlappingPairs.csv', sep="/"))

# apply filters on the overlapping results.
filteredNonOverlappingPairs = nonOverlappingPairs[which(nonOverlappingPairs$metric %in% accuracy_metrics),]
filteredNonOverlappingPairs = nonOverlappingPairs[which((nonOverlappingPairs$model1 %in% c("tm3", "tm2", "tm1") | nonOverlappingPairs$model2 %in% c("tm3", "tm2", "tm1"))) ,]
filteredNonOverlappingPairsIndices <- paste(filteredNonOverlappingPairs$model1, filteredNonOverlappingPairs$model2, filteredNonOverlappingPairs$metric, sep="-")

write.csv(filteredNonOverlappingPairs, paste(outputDir, 'filteredNonOverlappingPairs.csv', sep="/"))

print(filteredNonOverlappingPairs)
print(filteredNonOverlappingPairsIndices)

confidence_interval_graph_plots = list()
for (i in 1:length(accuracy_metrics)){
    g = accuracy_metrics[i]
    g_label <- toupper(g)
    selectedData <- df[df$metric_labels == g,]
    confidence_interval_graph_plots[[i]] <- ggplot(selectedData, aes(x = label, y = mean)) + 
    geom_errorbar(aes(ymin=lower, ymax=upper), colour="black", width=.1) +
    geom_point(size=2, shape=21, fill="black") + # 21 is filled circle
    xlab('') +
    ylab(g_label) +
    scale_x_discrete(breaks=selectedData$label, labels=as.vector(
    model_mapping$model_texts[match(selectedData$model_labels, model_mapping$model_names)])) +
    #ggtitle(paste(g_label, "- 84% Confidence Intervals", setp=""))+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 90, hjust = 1, face = "bold"))
    print(confidence_interval_graph_plots[[i]])
}

prow <- plot_grid( confidence_interval_graph_plots[[1]] + theme(legend.position="none"),
                   confidence_interval_graph_plots[[2]] + theme(legend.position="none"),
                   confidence_interval_graph_plots[[3]] + theme(legend.position="none"),
                   confidence_interval_graph_plots[[4]] + theme(legend.position="none"),
                   align = 'vh',
                   hjust = 0,
                   nrow = 2
                  )
#title <- ggdraw() + draw_label("Ranking Result for Cross Validation", fontface='bold')
confidence_interval_graphs <- plot_grid(prow, ncol = 1, rel_heights = c(.2, 1, .1), label_size=5)
print(confidence_interval_graphs)
ggsave(paste(outputDir, "confidence_interval_graphs.png", sep="/"), width=8, height=6)

# draw a partially ordered graph based on non-overlapping pairs


# for (i in 1:length(metric_labels)){
#     g = metric_labels[i]
#     selectedData <- df[df$metric_labels == g,]
#     p <- ggplot(selectedData, aes(x = labels, y = mean, ymin = lower, ymax = upper, fill = metric_labels)) +
#     geom_crossbar(width = 0.5, position = "dodge") +
#     #coord_flip() +
#     scale_x_discrete(breaks=selectedData$label, labels=as.vector(selectedData$model_labels)) +
#     xlab('model') +
#     ylab(g) +
#     ggtitle(g)
#     print(p)
# }


# Using the "sig_bs" results, create a graph to represent the direct graph for the models.
library(igraph)
for(metric_i in 1:length(accuracy_metrics)){
  #print(accuracy_metrics[metric_i])
  #if(accuracy_metrics[metric_i] == "predRange"){
  #  next
  #}
  #print(accuracy_metrics)
  selectedData <- nonOverlappingPairs[nonOverlappingPairs$metric == metric_labels[metric_i],]

  m <- matrix(0, nrow = length(model_names), ncol = length(model_names), byrow = FALSE)
  #colnames(m) <- names(models)
  #rownames(m) <- names(models)
  colnames(m) <- model_names
  rownames(m) <- model_names
  if(nrow(selectedData) > 0){
  for(i in 1:nrow(selectedData)){
    if(selectedData$direction[i] == "+"){
      m[as.character(selectedData$model1[i]), as.character(selectedData$model2[i])] = 1
    }else if(selectedData$direction[i] == "-"){
      m[as.character(selectedData$model2[i]), as.character(selectedData$model1[i])] = 1
    }
  }
  }
  
  edge_val <- c() 
  # if A -> B -> C, remove edge A -> C
  for(i in 1:length(model_names)){
    for(j in 1:length(model_names)){
      if(m[i,j] != 0){
        edge_val <- c(edge_val, m[i,j]) 
        for(k in 1:length(model_names)){
          if(m[j,k] != 0)
            m[i,k] = 0
        }
      }
    }
  }
  
  #plot the directed graph
  model_mean <- matrix(0, nrow = length(model_names), byrow = FALSE)
  rownames(model_mean) <- model_names
  colnames(model_mean) <- "mean"
  if(nrow(selectedData) > 0){
  for(i in 1:nrow(selectedData)){
    model_mean[which(rownames(model_mean) == selectedData[i,]$model1)] = round(selectedData[i,]$mean1, 3)
    model_mean[which(rownames(model_mean) == selectedData[i,]$model2)] = round(selectedData[i,]$mean2, 3)
  }
  }

  net=graph.adjacency(m,mode="directed",weighted=TRUE,diag=FALSE)
  
lo <- layout.fruchterman.reingold(net, niter = 1000)
plot(net, vertex.label=paste(model_mapping$model_texts[match(V(net)$name, model_mapping$model_names)], model_mean[which(rownames(model_mean) == V(net)$name)], sep = " : "), layout = lo, vertex.size = 5, vertex.frame.color = NULL, 
    vertex.label.dist = 1, vertex.label.cex = 0.7,  vertex.label.color="black", 
              edge.color="black", edge.arrow.size=0.5, edge.width = 0.5, edge.label.cex=0.7)
  
#plot.igraph(net,vertex.label=paste(V(net)$name, model_mean[which(rownames(model_mean) == V(net)$name)], sep = " : "), layout=layout.fruchterman.reingold(net)*30.0, vertex.color="white", vertex.label.color="black", vertex.size=3, edge.color="black", vertex.label.dist = 0.5, edge.label = edge_val, edge.width=3, edge.arrow.size=0.5, edge.arrow.width=1.2)
  
  title(main = accuracy_mapping[accuracy_mapping$accuracy_metrics == metric_labels[metric_i], "accuracy_metric_texts"])
}
```

```{r evaluate the p-values under family-wise control}

sig_bs <- familywiseHypoTest(iterationResults=iterResults, accuracy_metrics, model_names, "boot")
sig_bs = sig_bs[which(sig_bs$model1 %in% model_names | sig_bs$model2 %in% model_names),]

#sig_bs$model1 <- model_mapping$model_texts[match(sig_bs_f$model1, model_mapping$model_names)]
#sig_bs$model2 <- model_mapping$model_texts[match(sig_bs_f$model2, model_mapping$model_names)]

round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))

  df[,nums] <- round(df[,nums], digits = digits)

  (df)
}

write.csv(sig_bs,paste(outputDir, 'sig_bs.csv', sep="/"))
#print(sig_bs$p_value)

#print only pair comparisons that are related to transaction models
sig_bs_f = sig_bs[which(sig_bs$p_value < 0.05),]
sig_bs_f = sig_bs_f[which(sig_bs_f$metric %in% accuracy_metrics),]
sig_bs_f = sig_bs_f[order(sig_bs_f$p_value),]
sig_bs_f = round_df(sig_bs_f, 2)
#print(sig_bs_f$p_value)

#order models
sig_bs_f <- as.data.frame(t(apply(sig_bs_f, 1, function(x) {
  #print(x)
    if(x['direction'] == "-"){
      model_2 = x['model2']
      x['model2'] = x['model1']
      x['model1'] = model_2
      mean_2 = x['model2_mean']
      x['model2_mean'] = x['model1_mean']
      x['model1_mean'] = mean_2
      x['direction'] = "+"
      x['cohen_d'] = -as.numeric(x['cohen_d'])
      }
    x
  })))
#sig_bs_f$model1_mean = as.numeric(sig_bs_f$model1_mean)
#sig_bs_f$model2_mean = as.numeric(sig_bs_f$model2_mean)
#sig_bs_f$p_value = as.numeric(sig_bs_f$p_value)
#sig_bs_f$BH_p_value = as.numeric(sig_bs_f$BH_p_value)
#sig_bs_f$bonferroni_p_value = as.numeric(sig_bs_f$bonferroni_p_value)
#sig_bs_f$cohen_d = as.numeric(sig_bs_f$cohen_d)
sig_bs_f$model1 = model_mapping$model_texts[match(sig_bs_f$model1, model_mapping$model_names)]
sig_bs_f$model2 = model_mapping$model_texts[match(sig_bs_f$model2, model_mapping$model_names)]
#sig_bs_f_2$metric = accuracy_mapping[match(accuracy_mapping$accuracy_metrics == sig_bs_f_2$metric)]
print(sig_bs_f$cohen_d)
write.csv(sig_bs_f,paste(outputDir, 'sig_bs_f.csv', sep="/"))

sig_bs_f_1 = sig_bs_f[which(sig_bs_f$bonferroni_p_value < 0.05),]
sig_bs_f_1 = sig_bs_f_1[which(sig_bs_f_1$metric %in% accuracy_metrics),]
sig_bs_f_1 = sig_bs_f_1[order(sig_bs_f_1$bonferroni_p_value),]
sig_bs_f_1 = round_df(sig_bs_f_1, 2)
write.csv(sig_bs_f_1,paste(outputDir, 'sig_bs_bc.csv', sep="/"))

#identify the parirs that are not identified from the 84% overlaps.
sig_bs_tm = sig_bs_f[which(sig_bs_f$model1 %in% c("SWTI", "SWTII", "SWTIII") | sig_bs_f$model2 %in% c("SWTI", "SWTII", "SWTIII")),]
sig_bs_f_indices <- paste(sig_bs_tm$model1, sig_bs_tm$model2, sig_bs_tm$metric, sep="-")
print(sig_bs_f_indices)
sig_bs_tm$index <- sig_bs_f_indices
`%ni%` <- Negate(`%in%`)
filtered_sig_bs_tm = sig_bs_tm[which(sig_bs_tm$index %ni% filteredNonOverlappingPairsIndices), ]
write.csv(filtered_sig_bs_tm,paste(outputDir, 'filtered_sig_bs_tm.csv', sep="/"))

# Using the "sig_bs" results, create a graph to represent the direct graph for the models.
sig_rank_graph_plots = list()
library(igraph)
for(metric_i in 1:length(accuracy_metrics)){
  #print(accuracy_metrics[metric_i])
  #if(accuracy_metrics[metric_i] == "predRange"){
  #  next
  #}
  #print(accuracy_metrics)
  selectedData <- sig_bs[sig_bs$metric == metric_labels[metric_i],]
  m <- matrix(0, nrow = length(model_names), ncol = length(model_names), byrow = FALSE)
  #colnames(m) <- names(models)
  #rownames(m) <- names(models)
  colnames(m) <- model_names
  rownames(m) <- model_names
  for(i in 1:nrow(selectedData)){
    if(selectedData$p_value[i] < 0.05){
    if(selectedData$direction[i] == "+"){
      m[as.character(selectedData$model1[i]), as.character(selectedData$model2[i])] = round(selectedData$p_value[i], 3)
    }else if(selectedData$direction[i] == "-"){
      m[as.character(selectedData$model2[i]), as.character(selectedData$model1[i])] = round(selectedData$p_value[i], 3)
    }
    }
  }
  
  edge_val <- c() 
  # if A -> B -> C, remove edge A -> C
  for(i in 1:length(model_names)){
    for(j in 1:length(model_names)){
      if(m[i,j] != 0){
        edge_val <- c(edge_val, m[i,j]) 
        for(k in 1:length(model_names)){
          if(m[j,k] != 0)
            m[i,k] = 0
        }
      }
    }
  }
  
  #plot the directed graph
  model_mean <- matrix(0, nrow = length(model_names), byrow = FALSE)
  rownames(model_mean) <- model_names
  colnames(model_mean) <- "mean"
  for(i in 1:nrow(selectedData)){
    model_mean[which(rownames(model_mean) == selectedData[i,]$model1)] = round(selectedData[i,]$model1_mean, 3)
    model_mean[which(rownames(model_mean) == selectedData[i,]$model2)] = round(selectedData[i,]$model2_mean, 3)
  }

  net=graph.adjacency(m,mode="directed",weighted=TRUE,diag=FALSE)
  
lo <- layout.fruchterman.reingold(net, niter = 1000)
print(metric_i)
sig_rank_graph_plot = as.ggplot(
function() {
plot(net, vertex.label=paste(model_mapping$model_texts[match(V(net)$name, model_mapping$model_names)], model_mean[which(rownames(model_mean) == V(net)$name)], sep = " : "), layout = lo, vertex.size = 5, vertex.frame.color = NULL, 
    vertex.label.dist = 1, vertex.label.cex = 0.7,  vertex.label.color="black", 
              edge.color="black", edge.arrow.size=0.5, edge.width = 0.5, edge.label = edge_val, edge.label.cex=0.7)
title(main = accuracy_mapping[accuracy_mapping$accuracy_metrics == metric_labels[metric_i], "accuracy_metric_texts"])
}
)
print(sig_rank_graph_plot)
sig_rank_graph_plots[[metric_i]] = sig_rank_graph_plot
#plot.igraph(net,vertex.label=paste(V(net)$name, model_mean[which(rownames(model_mean) == V(net)$name)], sep = " : "), layout=layout.fruchterman.reingold(net)*30.0, vertex.color="white", vertex.label.color="black", vertex.size=3, edge.color="black", vertex.label.dist = 0.5, edge.label = edge_val, edge.width=3, edge.arrow.size=0.5, edge.arrow.width=1.2)
  
}

prow <- plot_grid( sig_rank_graph_plots[[1]] + theme(legend.position="none"),
                   sig_rank_graph_plots[[2]] + theme(legend.position="none"),
                   sig_rank_graph_plots[[3]] + theme(legend.position="none"),
                   sig_rank_graph_plots[[4]] + theme(legend.position="none"),
                   align = 'vh',
                   hjust = 0,
                   nrow = 2
                  )
#title <- ggdraw() + draw_label("Ranking Result for Cross Validation", fontface='bold')
sig_rank_graphs <- plot_grid(prow, ncol = 1, rel_heights = c(.2, 1, .1), label_size=5)
print(sig_rank_graphs)
ggsave(paste(outputDir, "sig_rank_graphs.png", sep="/"), width=6, height=10)


# filter for 

```

```{r stratified analysis, fig.width=4,fig.height=6, warning = FALSE}
projectCategories <- as.matrix(read.csv("./project_categorization1.csv"))
projectCategoryLabels <- paste(projectCategories[,1], projectCategories[,2], sep=": ")
print(projectCategoryLabels)
nCategories <- nrow(projectCategories)
benchmarkLabels <- paste("b", seq(1, nCategories, by=1), sep="")
categorizedBenchmarkResults = list()

#projectCategoryLabels <- as.data.frame(as.matrix(read.csv("./project_categorization1.csv")))
#projectCategoryLabels <- paste(projectCategoryLabels$Selection, projectCategoryLabels$Type, sep=": ")
categorizedBenchmarkResults1 = categorizedBenchmarkResults

for(i in 1:6){
  #print(i)
  #print(as.vector(projectCategories[i, ]))
  categorizedDataset <- selectData(dataset, selector=projectCategories[i,])

  #categorizedDataset <- selectData("dsets/combined_data_set_4_1.csv", c("type", "Entertainment"))
  #print(rownames(categorizedDataset))

  #categorizedDataset <- selectData("../android_analysis_datasets/android_dataset_6_29.csv", selector=c("initialDate","early"))
  
  #categorizedDataset <- selectData("../android_analysis_datasets/android_dataset_6_29.csv", selector=c("type","Productivity"))
  
  #print(categorizedDataset)
  benchmarkResults <- modelBenchmark(models, categorizedDataset)
  categorizedBenchmarkResults[[benchmarkLabels[i]]] <- benchmarkResults
  
  # calculate the rank information
  
}
#projectCategoryLabels <- as.data.frame(as.matrix(read.csv("./project_categorization1.csv")))
#projectCategoryLabels <- paste(projectCategoryLabels$Selection, projectCategoryLabels$Type, sep=": ")

p_cvAllRank_plots = list()
#print the categorized benchmark results
for(i in 1: nCategories){
benchmarkResults = categorizedBenchmarkResults[[names(categorizedBenchmarkResults)[i]]]
  
cvResults <- benchmarkResults$cvResults

cvAccuracyResults <- data.frame(cvResults$accuracyResults)
cvAccuracyResults$label <- rownames(cvAccuracyResults)
#cvAccuracyResults <- cvAccuracyResults[- grep("predRange", cvAccuracyResults$label),]
cvAccuracyResults <- cvAccuracyResults[cvAccuracyResults$label %in% accuracy_labels,]
cvAccuracyResults <- merge(cvAccuracyResults, model_mapping_2, by.x = "label", by.y="accuracy_labels", all=FALSE)
cvAccuracyResults$label <- NULL

#calculate ranking results
cvRankResults <- data.frame(model_names)
names(cvRankResults)<-c("model_labels")

for (j in 1:length(accuracy_metrics)){
  g = accuracy_metrics[j]
  selectedData <- cvAccuracyResults[cvAccuracyResults$metric_labels == g,]
  selectedData <- selectedData[,-3]#delete the metric_labels
  colnames(selectedData)<-c(g, "model_labels")
  if(g == "mmre" || g == "mdmre" || g == "mae"){
    selectedData[paste("rank", i, sep = "")] <- rank(selectedData[,1], ties.method = "min")
  }else{
    selectedData[paste("rank", i, sep = "")] <- rank(-selectedData[,1], ties.method = "min")
  }
  
  cvRankResults <- merge(cvRankResults, selectedData, by = "model_labels", all=FALSE)
}

#cvRankResults$model_labels = c("COSMIC", "IFPUG", "LASSO", "LOG SLOC", "NEURALNET", "REG TREE", "SLOC", "STEP LNR", "SWTI", "SWTII","SWTIII", "UCP")
#cvRankResults <- merge(cvRankResults, model_mapping, by.x = "model_labels", by.y="model_names", all=FALSE)

rownames(cvRankResults) <- model_mapping$model_texts[match(cvRankResults$model_labels, model_mapping$model_names)]
cvRankResults$model_labels = NULL

#make a total rank(rank*) base on the ranki
rank_sum <- vector(mode = "integer",length = length(model_names))
for (j in 1:length(model_names)){
  selectedData <- cvRankResults[j,]
  for(k in 1:length(accuracy_metrics)){
    rank_sum[j] <- rank_sum[j] + selectedData[,2*k]
  }
}
rank_sum <- rank(rank_sum, ties.method = "min")
#print(rank_sum)
cvRankResults["rank*"] <- rank_sum

cvRankResults <- cvRankResults[order(cvRankResults$'rank*'),]

#change the first line as the row name
#rownames(cvRankResults) = cvRankResults[,1]
#cvRankResults <- cvRankResults[,-1]

#print(round(cvRankResults,2))
# draw overall ranking histogram
selectedData <- cvRankResults[names(cvRankResults) == "rank*"]
names(selectedData) <- c("rank");
modelsName <- rownames(selectedData)
p_cvAllRank <- ggplot(selectedData, aes(x=modelsName, y=rank, fill=modelsName)) +
  geom_bar(stat="identity", colour = "black", width = 0.8, height=0.5) + 
  #scale_y_discrete(expand = c(0, 0)) + 
  guides(fill = guide_legend(title = "MODEL", nrow = 2)) +
  geom_text(aes(label = rank, vjust = -0.4, hjust = 0.5)) +
  ggtitle(projectCategoryLabels[i]) +
  #labs(caption=toupper("Total Rank")) + 
  theme(plot.caption = element_text(hjust=0.5, vjust=4, size=rel(0.2)), legend.position = "bottom", legend.text=element_text(size=8), legend.title=element_text(size=8),
        plot.title = element_text(hjust = 0.5, vjust=4, size=rel(0.8)), 
        #axis.line=element_blank(),
        axis.title=element_blank(), axis.text=element_blank(),axis.ticks=element_blank(),  panel.background = element_blank())
print(p_cvAllRank)
p_cvAllRank_plots[[i]] = p_cvAllRank
}

prow <- plot_grid( p_cvAllRank_plots[[1]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[2]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[3]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[4]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[5]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[6]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[7]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[8]] + theme(legend.position="none"),
                   p_cvAllRank_plots[[9]] + theme(legend.position="none"),
                   align = 'vh',
                   hjust = 0,
                   nrow = 3
                  )
legend_b <- get_legend(p[[1]] + theme(legend.position="bottom", legend.justification="center"))
title <- ggdraw() + draw_label("Ranking Result for Cross Validation", fontface='bold')
p_cvRank <- plot_grid(title, prow, legend_b, ncol = 1, rel_heights = c(.2, 1, .1), label_size=5)
print(p_cvRank)
ggsave(paste(outputDir, "p_cvRank.png", sep="/"), width=4, height=6)

#print(outputDir)

#9 categorized benchmarking results are produced
#1-3 are the projects of sizes: small, medium, and large
#4-6 are the projects of initialDate: early, normal, and late
#7-10 are the projects of different types: Game, Tools, Entertainment, Productivity.


```